# Saldae {data-navmenu="Intro"}

Row {data-width=200}
-----------------------------------------------------------------------
### Analysis Summary {data-commentary-height=200}

```{r,echo=FALSE,warning=FALSE,results='asis'}

h4(params$sald_report_asezwer)
```

***

```{r,echo=FALSE,warning=FALSE}
future_key_figures <- unlist(params$sald_predict_values$key_figures%>%purrr::map(~.x[[1]]))
future_key_figures <- data.frame(attribute = names(future_key_figures),forecast =future_key_figures)


```


### Key Figures ( Prediction)
```{r,echo=FALSE,warning=FALSE}


DT::datatable(future_key_figures,
              extensions = c('Buttons','Scroller'), options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE,
              dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
```


### Key figures (contribution)
```{r,echo=FALSE,warning=FALSE}
future_key_figures_pie <- future_key_figures%>%plotly::plot_ly( labels  = ~attribute, values= ~forecast, type = 'pie')

future_key_figures_pie
```




### Intro {data-commentary-height=400}

This is a template of interactive reporting output generated by [Saldae Analytics Platform](https://saldae-analytics.shinyapps.io/saldae-analytics-platform/).
If you want to learn more about us and our service please visit our website: 

[https://www.saldaeanalytics.com/](https://www.saldaeanalytics.com/)

*Total Sales of Beers in the following cities next month :* 

```{r,echo=FALSE,warning=FALSE}
future_key_figures_bar <- future_key_figures%>%plotly::plot_ly( y = ~attribute, x = ~forecast, type = 'bar',color = ~attribute, orientation = 'h')
future_key_figures_bar

```


***

### Useful concepts {data-commentary-height=300}


**Forecasting:**

Forecasting is required in many situations. Stocking an inventory may require forecasts of demand months in advance. Telecommunication routing requires traffic forecasts a few minutes ahead. Whatever the circumstances or time horizons involved, forecasting is an important aid in effective and efficient planning

***

